Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-02 paper_intersections.tex
Capitalize headings.

\subsubsection{Intersections on sides of $S_2$}
\label{sec:sides}

@@

\subsubsection{Intersections on edges of $S_3$}
\label{sec:edges}
\begin{algorithm}  
  \caption{2d-3d intersection, ICs on edges of $S_3$}
  \label{algo:collect_23_ip_edges}

@@

% Either all signs are equal ($S_2$ touching $S_3$) wee , or
% a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the 
% 
% 
% and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
% with faces of $S_3$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_2$ belongs to a face $f$ of $S_3$; we know from the order of the points
% whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
% Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
% intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
\subsubsection{Ordering of intersections}
\label{sec:ordering}
The final stage of the 2d-3d intersection is ordering of ICs. If there are less then 3 ICs in the list $I$ we merge lists $I$ and $J$ remove duplicities
and get at most 2 distinguish ICs forming a degenerate IP. Otherwise, we start with first IC $p$ in $I$, put it into final list $K$, 
get its successor \nface $x = F_p(p)$ and its successor IC $q=F_q(x)$. Unless $x$ is vertex of $S_2$, we put $q$ into $K$ and repeat the process until 
we pass all ICs in $I$.

@@

\subsection{Intersections between component meshes}
\label{sec:components}
We consider here the situation that components are in the interior of the 3d bulk mesh. After we compute
all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
If the bulk element intersects more than one component element, than we can create candidates from these.

@@

\subsection{Theoretical comparison}
Before presenting the results of our benchmarks, let us try to estimate the number of arithmetic operations performed during 1d-3d and 2d-3d element intersections
as we use different algorithms for the elementary line-triangle intersection. We consider 4 algorithms for the line-triangle intersections: \plucker algorithm 
described in Section \ref{sec:1d-2d}, the legacy code \ngh, the plane clipping algorithm due to Haines \cite{haines_fast_1991}, the minimum storage
algorithm due to Möller and Trumbore (MT) \cite{moller_fast_1997}. Raw numbers of arithmetic operations are summarized in Table \ref{tab:fundamental_flops}.
For the \plucker and \ngh we count FLOPS from the implementation of individual intersection algorithms, for Haines and MT we estimated FLOPS in theoretical 
implementation. In particular we account for reuse of the calculations in \plucker and Haines algorithms. Conclusions from this census are:
algorithms based on the \plucker coordinates should be competitive with state of art algorithms in the case of 1d-3d and 2d-3d intersections. The expected performance
for the 1d-2d case seems to be poor however these intersections are computed after 1d-3d and 2d-3d so the \plucker coordinates may be reused, then we get 
quite competitive $45$ FLOPS. Similarly we may expect better times in remaining two intersection cases when we account for the reuse of calculation between elements.
Compared to the legacy code \ngh the \plucker algorithm for 1d-3d should be about $2.5\times$ faster and the 2d-3d about $5\times$ faster.

>>>>

\subsubsection{Intersections on Sides of $S_2$}
\label{sec:sides}

@@

\subsubsection{Intersections on Edges of $S_3$}
\label{sec:edges}
\begin{algorithm}  
  \caption{2d-3d intersection, ICs on edges of $S_3$}
  \label{algo:collect_23_ip_edges}

@@

% Either all signs are equal ($S_2$ touching $S_3$) wee , or
% a single edge have the sign oposite to other twotwo edges have a sign oposite then the thi. of According to the 
% 
% 
% and need to insert them into $I$ to correct place. To this end we exploit additional information about coincidence of points
% with faces of $S_3$. Every point $p$ from the first part of the algorithm \notePE{I would use proper references instead, I got confused, what 'part of algorithm' is..} that is not a vertex of $S_2$ belongs to a face $f$ of $S_3$; we know from the order of the points
% whether the face comes before or after the point in the intersection polygon; in the first case we set $F[0,f] =p$, in the second case we set $F[1,f]=p$. 
% Every point $p$ from the second part of the algorithm lies on an edge $e$ which is between two faces $f_0$, $f_1$. The correct order of the faces on the 
% intersection polygon is determined by the sign of the edge-triangle intersection. So, having the faces in the correct order we set $F[0,f_0]=p$ and $F[1, f_1]=p$.
\subsubsection{Ordering of Intersections}
\label{sec:ordering}
The final stage of the 2d-3d intersection is ordering of ICs. If there are less then 3 ICs in the list $I$ we merge lists $I$ and $J$ remove duplicities
and get at most 2 distinguish ICs forming a degenerate IP. Otherwise, we start with first IC $p$ in $I$, put it into final list $K$, 
get its successor \nface $x = F_p(p)$ and its successor IC $q=F_q(x)$. Unless $x$ is vertex of $S_2$, we put $q$ into $K$ and repeat the process until 
we pass all ICs in $I$.

@@

\subsection{Intersections Between Component Meshes}
\label{sec:components}
We consider here the situation that components are in the interior of the 3d bulk mesh. After we compute
all component-bulk intersections, we use it to easily find all the component-component intersection candidates.
If the bulk element intersects more than one component element, than we can create candidates from these.

@@

\subsection{Theoretical Comparison}
Before presenting the results of our benchmarks, let us try to estimate the number of arithmetic operations performed during 1d-3d and 2d-3d element intersections
as we use different algorithms for the elementary line-triangle intersection. We consider 4 algorithms for the line-triangle intersections: \plucker algorithm 
described in Section \ref{sec:1d-2d}, the legacy code \ngh, the plane clipping algorithm due to Haines \cite{haines_fast_1991}, the minimum storage
algorithm due to Möller and Trumbore (MT) \cite{moller_fast_1997}. Raw numbers of arithmetic operations are summarized in Table \ref{tab:fundamental_flops}.
For the \plucker and \ngh we count FLOPS from the implementation of individual intersection algorithms, for Haines and MT we estimated FLOPS in theoretical 
implementation. In particular we account for reuse of the calculations in \plucker and Haines algorithms. Conclusions from this census are:
algorithms based on the \plucker coordinates should be competitive with state of art algorithms in the case of 1d-3d and 2d-3d intersections. The expected performance
for the 1d-2d case seems to be poor however these intersections are computed after 1d-3d and 2d-3d so the \plucker coordinates may be reused, then we get 
quite competitive $45$ FLOPS. Similarly we may expect better times in remaining two intersection cases when we account for the reuse of calculation between elements.
Compared to the legacy code \ngh the \plucker algorithm for 1d-3d should be about $2.5\times$ faster and the 2d-3d about $5\times$ faster.
